% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice. 

\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\setbeamersize{text margin left=1cm,text margin right=1cm} 


\title{Secure Deduplication Across Files}

% A subtitle is optional and this may be deleted
%\subtitle{Optional Subtitle}

\author{Nithin V Nath }
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.


\institute[] % (optional, but mostly needed)
{
	Advisor: Dr. Bhavana Kanukurthi\\\vspace*{2mm}
	Department of Computer Science and Automation\\
	Indian Institute of Science
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date{23-Jun-2016}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{Cryptography}
% This is only inserted into the PDF information catalog. Can be left
% out. 

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}

\subsection{Deduplication}

\begin{frame}{Deduplication}{}
  \begin{itemize}
  \setlength\itemsep{1em}
  \item {
    Large amount of data stored in cloud storage.
  }
  \item {
    Multiple users store the same file.
  }
  \item {
    Service providers need to employ space saving techniques to keep cost down.
  }
	\begin{definition}
		Technique that enables storage providers to store a single copy of the data.
	\end{definition}
  \end{itemize}
\end{frame}

\subsection{Deduplication Example}

% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{Deduplication in Action}
  \begin{itemize}
  \setlength\itemsep{1em}
  \item {
    Alice uploads a file $M$ to the server $S$.
    \pause % The slide will pause after showing the first item
  }
  \item {   
	 Bob requests to upload his copy of the same file $M$ to $S$.
  }
  % You can also specify when the content should appear
  % by using <n->:
  \item<3-> {The server identifies
	that $M$ is already stored and simply updates the metadata associated with $M$ to show
	that the file is owned by both Alice and Bob.
  }
  \item Make this an image
  \end{itemize}
\end{frame}

\subsection{Secure Deduplication}


\begin{frame}{Secure Deduplication}
\begin{itemize}
	\setlength\itemsep{1em}
	\item Deduplication along with privacy is a conflicting idea
	\item Users would like their data to be encrypted
	
	\item Storage providers would like to identify the file uploaded by user
		to enable deduplication.
\end{itemize}
\end{frame}

\begin{frame}{Motivation}
\begin{itemize}
	\setlength\itemsep{1em}
	\item Photos taken one after the other are often \textit{almost} identical to each other.
	\item These multiple files are not supported in traditional file level deduplication.
	\item \textbf{Challenge}: Identify that plaintexts underneath these ciphertexts are 
		close to each other and store only the difference.
\end{itemize}
\end{frame}

\begin{frame}{Problem Statement}
	\begin{itemize}
	\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\subsection{Related Work}

\begin{frame}{Related Work}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item Convergent Encryption (year?)
		\item Message Locked Encryption
		\item Interactive Message Locked Encryption
	\end{itemize}

\end{frame}

\begin{frame}{Convergent Encryption}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item Deterministic cryptosystem that produces  identical ciphertext files from identical plaintext files.
		\item $K = H(M)$
		\item $C = E(K, M)$
		\item $M = D(K,C)$
	\end{itemize}
\end{frame}

\begin{frame}{Message Locked Encryption}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Interactive Message Locked Encryption}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\subsection{Preliminaries}

\begin{frame}{Entropy}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Statistical Distance}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Extractors}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Deterministic Encryption}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item Why is this meaningful in this setting?
	\end{itemize}
\end{frame}

\begin{frame}{Error Correcting Codes}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\subsection{Contributions}

\begin{frame}{Our Work}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\subsection{Road-map}
\begin{frame}{Road-map}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\section{Construction}
\begin{frame}{Setting}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Adversarial Model}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Games}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item 
	\end{itemize}
\end{frame}



\begin{frame}{Blocks}
\begin{block}{Block Title}
You can also highlight sections of your presentation in a block, with it's own title
\end{block}
\begin{theorem}
There are separate environments for theorems, examples, definitions and proofs.
\end{theorem}
\begin{example}
Here is an example of an example block.
\end{example}
\end{frame}

% Placing a * after \section means it will not show in the
% outline or table of contents.
\section*{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}
  
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}



% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{For Further Reading}
    
  \begin{thebibliography}{10}
    
  \beamertemplatebookbibitems
  % Start with overview books.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.
 
    
  \beamertemplatearticlebibitems
  % Followed by interesting articles. Keep the list short. 

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

\end{document}


\grid
